---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "## ",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


```{r, include=FALSE}
options("width"=100)
tmp <- devtools:::read_dcf("DESCRIPTION")
```

```{r, results='asis', echo=FALSE}
cat("#", tmp$Title)
```


## Status


[![Travis-CI Build Status](https://api.travis-ci.com/petermeissner/stringb.svg?branch=master)](https://www.travis-ci.com/github/petermeissner/stringb)
[![codecov](https://codecov.io/gh/petermeissner/stringb/branch/master/graph/badge.svg)](https://codecov.io/gh/petermeissner/stringb/tree/master/R)
[![CRAN version](http://www.r-pkg.org/badges/version/stringb)](https://cran.r-project.org/package=stringb)
![CRAN downloads](https://cranlogs.r-pkg.org/badges/grand-total/stringb)



**Version**

```{r, results='asis', echo=FALSE}
cat(tmp$Version)
```


**License**

```{r, results='asis', echo=FALSE}
cat(tmp$License, "<br>")
cat(as.character(eval(parse(text=tmp$Author))))
```



**Description**

```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```



**This packages aims at:**

- **no dependencies** except what comes with base-R (i.e. there shall be no compilation needed) 
- for good or worse relying on base-R text handling mechanisms means getting **base-R regular expression engine including the Perl mode**
- writing **text handling functions as generics** so that methods for all kind of 
  structures containing text can be added 
- providing functions that allow for different character encodings 
- but rigorously defaulting to UTF-8 as expected input and default output 
  thereby enhancing cross platform cooperation
- adding more power to general basic text handling functions by additional 
  options (e.g. the text_read() function allows to read in and tokenize text in 
  one function call)
- and insisting on a **flat interface** - meaning that all functionality should come from functions and plain parameters (in contrast to e.g. parameters that need specialized functions or functions outputs to perform)
- adding further general text handling tools if there is a general enough 
  purpose for the added function(ality)
  

**This package does not aim at:**

- being fast (fast is good but will not be traded for the above listed aims - stringi might be your friend here)
- being ultimately compatible (compatible is good but again will not be traded for the above listed aims - again stringi might be your solution in that case)


## Contribution

Note, that this package uses a Contributor Code of Conduct. By participating in this project you agree to abide by its terms: http://contributor-covenant.org/version/1/0/0/ (basically this should be a place were people get along with each other respectful and nice because it's simply more fun that way for everybody)

Contributions are very much welcome, e.g. in the form of:

- **typo fixing** ([edit file directly on Github](https://help.github.com/articles/editing-files-in-another-user-s-repository/))
- **bug reporting** (file an [issue](https://guides.github.com/features/issues/) - after having searched if the issue came up before - as - if possible - [minimal reproducable example](http://stackoverflow.com/help/mcve))
- **extending help files** (e.g. [edit the respective files directly on Github](https://help.github.com/articles/editing-files-in-another-user-s-repository/) or [fork the package](https://help.github.com/articles/fork-a-repo/) and later on make a [pull request](https://help.github.com/articles/using-pull-requests/); note, that the package use [roxygen2](http://r-pkgs.had.co.nz/man.html) for easing documentation)
- **writing example** (e.g. [edit the respective files directly on Github](https://help.github.com/articles/editing-files-in-another-user-s-repository/) or [fork the package](https://help.github.com/articles/fork-a-repo/) and later on make a [pull request](https://help.github.com/articles/using-pull-requests/); note, that the package use [roxygen2](http://r-pkgs.had.co.nz/man.html) for easing documentation)
- **vignette writing** (file an [issue](https://guides.github.com/features/issues/) first so that we can discuss things than [fork the package](https://help.github.com/articles/fork-a-repo/) and later on make a [pull request](https://help.github.com/articles/using-pull-requests/))
- **test writing** (have a look at the [test coverage](https://codecov.io/gh/petermeissner/stringb/tree/master/R) than [fork the package](https://help.github.com/articles/fork-a-repo/) and later on make a [pull request](https://help.github.com/articles/using-pull-requests/))
- **feature suggestions** (file an [issue](https://guides.github.com/features/issues/) describing the idea, why this is important, possible alternative solutions and an example)
- **general discussion** of approach and or implementation  (file an [issue](https://guides.github.com/features/issues/))
- implementation **improvements** (file an [issue](https://guides.github.com/features/issues/) naming whats to be improved, why and how)


## Installation


**dev version**
```{r, eval=FALSE}
devtools::install_github("petermeissner/stringb")
library(stringb)
```


**stable version**
```{r, eval=FALSE}
install.packages("stringb")
library(stringb)
```


## Function list

```{r}
library(stringb)
objects("package:stringb")
```

    

## Example Usage

```{r}
library(stringb)
(test_file <- stringb:::test_file("rc_1_ch1.txt")) # just a file accompanying the package to test things

text_read( test_file, tokenize = "\\W", n=20)[67:79]
```

Although, text_read() is just a wrapper around readLines() it has become more powerful, consistent and streamlined by (1) always producing UTF-8 encoded character vectors, (2) allowing the usage of all readLines() options - e.g. n, (3) and adding further useful functionality like on-the-fly-tokenization.


```{r plot1}
library(stringb)
(test_file <- stringb:::test_file("rc_3.txt")) # just a file accompanying the package to test things

text          <- text_read(test_file, tokenize = "\\W+")
friday_occurs <- text_detect(text, "FRIDAY", ignore.case=TRUE)

plot(friday_occurs, type = "n")
abline(v=which(friday_occurs))
title("Friday Appearing in Robinson Crusoe")

```

Text_detect() is another example for a streamlined interface (easier to remember than grepl) with all base-R whistles and bells still being there - almost all base-R pattern matching functions have the ignore.case options to make pattern matching case insensitive. 


```{r plot2}
library(stringb)
(test_file <- stringb:::test_file("rc_3.txt")) # just a file accompanying the package to test things
text          <- text_read(test_file)

plot(text, pattern="Friday", ignore.case=TRUE)
```



A simple method to plot character vectors with pattern markup was added as well. 
    
    
    
    
    
    
    
    
    
